### 2019-04-18 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
I don't know how to talk about Sumit et al work in limited space

The purpose of this work is not to optimize on the index policy, but rather propose new ways of using indices in a decentralized setting,
% And for some configurations, using a decentralized approach with a more efficient index family (\klUCB{} instead of \UCB) has better performances than the centralized approach.
and as we observed that using \klUCB{} rather than \UCB{} indices always yield better practical performance,
from now on we only report results for \klUCB.
%, as the theoretical guarantees for single player suggested,

@@

We present results for two bandit instance: one with $K=3$ arms and means
$\boldsymbol{\mu} = [0.1, 0.5, 0.9]$, for which two cases $M=2$ and $M=3$ are presented in Figure~\ref{fig:5:selfish_fail1}. For the second instance $K=9$ and $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$,
three cases are presented: $M=6$ in Figure~\ref{fig:5:MP__K9_M6_T10000_N1000__4_algos},
and for the two limit cases $M=2$ and $M=9=K$ in Figure~\ref{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}.
%
We also include histograms showing the \emph{distribution} of regret at $t=T$,
as this allows to check if the regret is indeed small for \emph{each} run of the simulation.
%
For the plots showing the regret, our \emph{asymptotic} lower bound from Theorem~\ref{thm:5:BetterLowerBound} is displayed.

@@

% Dynamic settings, when $M$ can change in time,
% were considered in the analysis of both
In the presence of sensing (observation model \modeldeux), we also compared our algorithms to  %multi-player multi-armed bandits algorithms
with \MEGA{} \citep{Avner15} and \MusicalChair{} \citep{Rosenski16}. Yet these two algorithms were found hard to use efficiently in practice and we show in
% that were also proposed
%
Figure~\ref{fig:5:MP__K9_M3_T123456_N100__8_algos} that they perform poorly in comparison to \rhoRand, \RandTopM{} and \MCTopM.
%
\MEGA{} needs a careful tuning of \emph{five} parameters ($c$, $d$, $p_0$, $\alpha$ and $\beta$) to attain reasonable performances. No good guideline for tuning them is provided and using \emph{cross validation}, as suggested by \cite{Avner15},
can be considered out of the scope of \emph{online} sequential learning.
%In practice, on a fixed instance, the authors do not indicate how to select the parameters, even with a perfect knowledge of the parameters ($\boldsymbol{\mu}$ and $T$).
%
\MusicalChair{} consists of a random exploration phase of length $T_0$ after which the players quickly converge to orthogonal strategies targeting the $M$ best arms. With probability $1-\delta$, its regret is proved to be ``constant'' (of order $\log(1/\delta)$). The theoretical minimal value for $T_0$ depends on $\delta$, on the horizon $T$ and on a lower bound $\epsilon$ on the gap $\Delta = \mu^*_M - \mu^*_{M+1}$, and the practical tuning is hard too. %% which are both unavailable in our setting.

>>>>

The purpose of this work is not to optimize on the index policy, but rather propose new ways of using indices in a decentralized setting,
% And for some configurations, using a decentralized approach with a more efficient index family (\klUCB{} instead of \UCB) has better performances than the centralized approach.
and as we observed in Table~\ref{table:5:comparisonUCB_klUCB} that using \klUCB{} rather than \UCB{} indices always yield better practical performance,
from now on we only report results for \klUCB.
%, as the theoretical guarantees for single player suggested,

@@

We present results for two bandit instances: one with $K=3$ arms and means
$\boldsymbol{\mu} = [0.1, 0.5, 0.9]$, for which two cases $M=2$ and $M=3$ are presented in Figure~\ref{fig:5:selfish_fail1}. For the second instance $K=9$ and $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$,
three cases are presented: $M=6$ in Figure~\ref{fig:5:MP__K9_M6_T10000_N1000__4_algos},
and for the two limit cases $M=2$ and $M=9=K$ in Figure~\ref{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}.
%
We also include histograms showing the \emph{distribution} of regret at $t=T$,
as this allows to check if the regret is indeed small for \emph{each} run of the simulation.
%
For the plots showing the regret, our \emph{asymptotic} lower bound from Theorem~\ref{thm:5:BetterLowerBound} is displayed.

@@

% Dynamic settings, when $M$ can change in time,
% were considered in the analysis of both
We also compared our algorithms to  %multi-player multi-armed bandits algorithms
with \MEGA{} \citep{Avner15} and \MusicalChair{} \citep{Rosenski16}, in the presence of sensing, \ie, observation model \modeldeux, for which they were developed.
Yet these two algorithms were found hard to use efficiently in practice and we show in
% that were also proposed
%
Figure~\ref{fig:5:MP__K9_M3_T123456_N100__8_algos} that they perform poorly in comparison to \rhoRand, \RandTopM{} and \MCTopM.
%
\MEGA{} needs a careful tuning of \emph{five} parameters ($c$, $d$, $p_0$, $\alpha$ and $\beta$) to attain reasonable performances. No good guideline for tuning them is provided and using \emph{cross validation}, as suggested by \cite{Avner15},
can be considered out of the scope of \emph{online} sequential learning.
%In practice, on a fixed instance, the authors do not indicate how to select the parameters, even with a perfect knowledge of the parameters ($\boldsymbol{\mu}$ and $T$).
%
\MusicalChair{} consists of a random exploration phase of length $T_0$ after which the players quickly converge to orthogonal strategies targeting the $M$ best arms. With probability $1-\delta$, its regret is proved to be ``constant'' (of order $\log(1/\delta)$). The theoretical minimal value for $T_0$ depends on $\delta$, on the horizon $T$ and on a lower bound $\epsilon$ on the gap $\Delta = \mu^*_M - \mu^*_{M+1}$, and the practical tuning is hard too. %% which are both unavailable in our setting.

### 2019-04-18 2-Chapters/5-Chapter/chapter5.tex
I don't know how to talk about Sumit et al work in limited space

Inspired by our article \cite{Besson2018ALT},
Boursier and Perchet studied this question in the summer $2018$ following its publication \cite{BoursierPerchet18}.
Their answer is that the model without sensing information is essentially not harder than the model with sensing information.
%
Similarly, Lugosi and Mehrabian studied the same problem \cite{LugosiMehrabian18}.
In both works, the authors detail algorithms that are unfortunately suboptimal empirically, but give in both cases a logarithmic regret if $M \leq K$ players all independently implement the proposed algorithm.

@@

The results presented in \cite{LugosiMehrabian18} are based on some hypotheses, for instance the tuning they propose for the length $g$ of the uniform exploration phase in the beginning of their ``Musical Chair''-like algorithm is based on a prior knowledge of the horizon $T$.
In Section~4 they explain how to relax the assumptions of their results.
For the same example, the ``doubling trick'' technique can be used to obtain a regret upper bound for an algorithm unaware of the value of $T$, within a constant multiplicative factor of the upper bound given for the algorithm aware of $T$ (Section~4.1). Because the regret bound is of the form $\bigO{\sqrt{T} \log(T)}$, a simple ``doubling trick'' of increasing horizons of lengths $T_i = 2^i$ works well, as proposed in \cite{CesaLugosi06} and as studied in depth in our article \cite{Besson2018DoublingTricks}, and quickly presented in Appendix~\ref{app:2:DoublingTricks}.
%
They also study in Section~4.3 an extension of the model for the case with more players than arms, but we do not give more details on this aspect. Their definition of a centralized regret for this case is an interesting and natural generalization of our definition, and they also proposed an algorithm achieving $\bigO{M K \log(T) \exp(4M/K) / \Delta^2}$ regret in this case.
Finally, they also proposed in Section~4.4 an extension of their algorithm to estimate the number of players $M$, which is analyzed as for the Musical Chair algorithm in \cite{Rosenski16}, and also achieve logarithmic regret.
Note that it is significantly harder to estimate $M$ without collision information, and Algorithm~3 in page 24 is quite complex.
We did not implement it, and it is an interesting future work to run some numerical simulations in order to validate it empirically.

@@

To illustrate the difficulty of the ``no sensing'' case, we illustrate here the performances of different algorithms designed specifically for this setting.
As above, we consider a bandit problem with $K=9$ arms, of means $0.1,0.2,\dots,0.8,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and an horizon of $T=10000$.
We include the \Selfish-\klUCB{} algorithm as an heuristic, as well as the Improved \MusicalChair{} algorithm from \cite{LugosiMehrabian18} and \textsc{Sic-MMAB} from \cite{BoursierPerchet18}.
The centralized multiple-play \klUCB{} is included as an unrealistic efficient baseline, but it is interesting to also add it here, as it does not use the sensing information but only the joint information (the reward) $r^j(t)$, because it directly affects the player in an orthogonal configuration and thus never encounters any collision (thus $r^j(t)=Y_{t,A^j(t)}$ for each $j,t$).
%
For the two other algorithms, we use the parameters advised in all papers: for \textsc{Sic-MMAB}, we used $T_0 = \lceil K \log(T) \rceil$ as advised by the authors.
For Improved-MC, we used $c=1$ which gives $g=235$, whereas in the paper the authors use $c=128$ for their analysis. We found empirically no difference when using different values of the constant $c$ or $g$, and unfortunately the regret of Improved-MC was always found to be linear (\eg, $12150$ for $T=10000$).

@@

We give in Table~\ref{table:5:meanRegretSimulationsNoSensing}, we give the mean regret obtained for these different algorithms, and we observe a drastic difference between the unrealistic centralized algorithm, which achieves a very small regret, the heuristic \Selfish-\klUCB{} which achieve small mean regret (but is small to fail in theory and in some instances), and the two other algorithms.
We were unable to find any bug in our implementation of Improved \MusicalChair{} from \cite{LugosiMehrabian18} and all the different tuning of $c$ (or $g$) explored gave the same disappointing result (linear regret).
The \textsc{Sic-MMAB} algorithm performs better than the \Selfish{} heuristic for the extreme case of $M=K$, but its large regret in this case shows that the orthogonalization protocol developed by \cite{BoursierPerchet18} is not fast to converge (for illustration, for the same problem for $M=K=9$ for the ``sensing'' case, \MCTopM-\klUCB{} achieves a mean regret of about $40$, two orders of magnitude smaller!).
%
Further empirical evaluation would be needed to fully understand the situation, and a first future work would be to fix the algorithm proposed by \cite{LugosiMehrabian18} and illustrate in some problems that it can indeed achieve sub-linear regret (maybe it does but only for large horizons, even if we did try larger values of $T$ like up-to $T=200000$).

@@

Clearly, the problem is easier by allowing communication, and it is quite immediate to see that the communication capacity between players must be limited otherwise the problem is already known and solved.
Indeed, imagine that at each time step $t$, all the $M$ players could share an unbounded number of bits with the other players, at no cost, even if this hypothesis is clearly unrealistic for wireless networks.
Then they can share all their observations, and they can all run the same multiple-plays MAB algorithm \cite{Anantharam87a} (in a deterministic way), like for instance the extension of Thompson sampling for multiple-plays studied in \cite{Komiyama15}, or extensions of \KLUCB{} from \cite{Luedtke16}.
In this setting, a logarithmic regret is obtained easily, and the regret upper-bound of the two aforementioned algorithms asymptotically achieve the lower-bound from \cite{Anantharam87a}.

@@

In \cite{Rosenski16}, the authors explain that if the model allows arrival or departures of players at \emph{any time step}, then the game is much harder, and sub-linear regret is most likely un-achievable, if we consider the natural extension of the definition of regret as in our model presented in Section~\ref{sec:5:model} above.
However, this negative results depends on how arrival of players are modeled:
if an arriving player has no prior memory of the previous observations, \ie, if it model a new device, then if there is no restriction on the number or frequency of arrival or departures, we can most likely prove that sub-linear regret is not achievable in general.
A simple but extreme example shows that regret has to be linear for any bandit strategy (in the observation model with sensing).
Consider $K=2$ Bernoulli-distributed arms of means $\mu_1=\mu_2=1/2$, and one player is always active and play any bandit strategy (\eg, \MCTopM-\klUCB).
Every time step, another player is either arriving, without any knowledge of the problem (\eg, it is a fresh and new IoT device). Then no matter the strategy of these news players, even if they all play \MCTopM-\klUCB{} for instance, if they player a uniformly-efficient strategy there is a non-zero probability that player $1$ suffer from a collision at each time step, thus resulting in linear centralized system regret.

>>>>

Inspired by our article \cite{Besson2018ALT},
Boursier and Perchet studied this question in the summer $2018$ following its publication \cite{BoursierPerchet18}.
Their answer is that the model without sensing information is essentially not harder than the model with sensing information.
%
Similarly, Lugosi and Mehrabian studied the same problem \cite{LugosiMehrabian18}.
In both works, the authors detail algorithms that give in both cases a logarithmic regret if $M \leq K$ players all independently implement the proposed algorithm.

@@

The results presented in \cite{LugosiMehrabian18} are based on some hypotheses, for instance the tuning they propose for the length $g$ of the uniform exploration phase in the beginning of their ``Musical Chair''-like algorithm is based on a prior knowledge of the horizon $T$.
In Section~4 they explain how to relax the assumptions of their results.
For the same example, the ``doubling trick'' technique can be used to obtain a regret upper bound for an algorithm unaware of the value of $T$, within a constant multiplicative factor of the upper bound given for the algorithm aware of $T$ (Section~4.1). Because the regret bound is of the form $\bigO{\sqrt{T} \log(T)}$, a simple ``doubling trick'' of increasing horizons of lengths $T_i = 2^i$ works well, as proposed in \cite{CesaLugosi06} and as studied in depth in our article \cite{Besson2018DoublingTricks}, and quickly presented in Appendix~\ref{app:2:DoublingTricks}.
%
They also study in Section~4.3 an extension of the model for the case with more players than arms, but we do not give more details on this aspect. Their definition of a centralized regret for this case is an interesting and natural generalization of our definition, and they also proposed an algorithm achieving $\bigO{M K \log(T) \exp(4M/K) / \Delta^2}$ regret in this case.
Finally, they also proposed in Section~4.4 an extension of their algorithm to estimate the number of players $M$, which is analyzed as for the Musical Chair algorithm in \cite{Rosenski16}, and also achieve logarithmic regret.
Note that it is significantly harder to estimate $M$ without collision information, and Algorithm~3 in page 24 is quite complex.
We did not implement it, and it would be interesting to run some numerical simulations in order to validate it empirically.

@@

To illustrate the difficulty of the ``no sensing'' case, we illustrate here the performances of different algorithms designed specifically for this setting.
As above, we consider a bandit problem with $K=9$ arms, of means $0.1,0.2,\dots,0.8,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and an horizon of $T=10000$.
We include the \Selfish-\klUCB{} algorithm as an heuristic, as well as the Improved \MusicalChair{} algorithm from \cite{LugosiMehrabian18} and \textsc{Sic-MMAB} from \cite{BoursierPerchet18}.
The centralized multiple-play \klUCB{} is included as an unrealistic efficient baseline, but it is interesting to also add it here, as it does not use the sensing information but only the joint information (the reward) $r^j(t)$, as it directly affects the player in an orthogonal configuration and thus never encounters any collision (thus $r^j(t)=Y_{t,A^j(t)}$ for each $j,t$).
%
For the two other algorithms, we use the parameters advised in all papers: for \textsc{Sic-MMAB}, we used $T_0 = \lceil K \log(T) \rceil$ as advised by the authors.
For Improved-MC, we used $c=1$ which gives $g=235$, whereas in the paper the authors use $c=128$ for their analysis. We found empirically no difference when using different values of the constant $c$ or $g$, and unfortunately the regret of Improved-MC was always found to be linear\footnote{For instance Improved-MC obtained a mean regret $12150$ for $T=10000$, for $M=3,K=9$, but seeing one value for one horizon does not mean anything, however we also experimented with larger values of $T$ and found a same linear behavior.}.

@@

We give in Table~\ref{table:5:meanRegretSimulationsNoSensing}, we give the mean regret obtained for these different algorithms, and we observe a drastic difference between the unrealistic centralized algorithm, which achieves a very small regret, the heuristic \Selfish-\klUCB{} which achieve small mean regret (but is small to fail in theory and in some instances), and the two other algorithms.
We were unable to find any bug in our implementation of Improved \MusicalChair{} from \cite{LugosiMehrabian18} and all the different tuning of $c$ (or $g$) explored gave the same disappointing result (linear regret).
The \textsc{Sic-MMAB} algorithm performs better than the \Selfish{} heuristic for the extreme case of $M=K$, but its large regret in this case shows that the orthogonalization protocol developed by \cite{BoursierPerchet18} is not fast to converge (for illustration, for the same problem for $M=K=9$ for the ``sensing'' case, \MCTopM-\klUCB{} achieves a mean regret of about $40$, two orders of magnitude smaller!).
%
Further empirical evaluation would be needed to fully understand the situation, and a first future work would be to either fix our implementation of the algorithm proposed by \cite{LugosiMehrabian18} or propose an efficient modification, and illustrate in some problems that it can indeed achieve sub-linear regret (maybe it does but only for large horizons, even if we did try larger values of $T$ like up-to $T=200000$).

@@

Clearly, the problem is easier by allowing communication, and it is quite immediate to see that the communication capacity between players must be limited otherwise the problem is already known and solved.
Indeed, imagine that at each time step $t$, all the $M$ players could share an unbounded number of bits with the other players, at no cost, even if this hypothesis is clearly unrealistic for wireless networks.
Then they can share all their observations, and they can all run the same multiple-plays MAB algorithm \cite{Anantharam87a}, like for instance the extension of Thompson sampling for multiple-plays studied in \cite{Komiyama15}, or extensions of \KLUCB{} from \cite{Luedtke16}.
In this setting, a logarithmic regret is obtained easily, and the regret upper-bound of the two aforementioned algorithms asymptotically achieve the lower-bound from \cite{Anantharam87a}.

@@

In \cite{Rosenski16}, the authors explain that if the model allows arrival or departures of players at \emph{any time step}, then the game is much harder, and sub-linear regret is most likely un-achievable, if we consider the natural extension of the definition of regret as in our model presented in Section~\ref{sec:5:model} above.
However, this negative results depends on how arrival of players are modeled:
if an arriving player has no prior memory of the previous observations, \ie, if it model a new device, then if there is no restriction on the number or frequency of arrival or departures, we can most likely prove that sub-linear regret is not achievable in general.
A simple but extreme example shows that regret has to be linear for any bandit strategy (in the observation model with sensing).
Consider $K=2$ Bernoulli-distributed arms of means $\mu_1=\mu_2=1/2$, and one player is always active and play any bandit strategy (\eg, \MCTopM-\klUCB).
Every time step, another player is either arriving, without any knowledge of the problem (\eg, it is a fresh and new IoT device). Then no matter the strategy of these news players, even if they all play \MCTopM-\klUCB{} for instance, if they play a uniformly-efficient strategy there is a non-zero probability that player $1$ suffer from a collision at each time step, thus resulting in linear centralized system regret.
